Addition and removal energies of circular quantum dots

### 2017-08-30 Manuscript/paper.tex
Explain how commutator truncation in IM-SRG affects final results

In this paper, we truncate both $\hat{H}$ and $\hat{\eta}$ at the two-body level, leading to an approach known as IM-SRG(2).  This normal-ordered two-body approximation appears to be sufficient in many cases and has yielded excellent results for several nuclei \cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.

>>>>

In this paper, we truncate both $\hat{H}$ and $\hat{\eta}$ at the two-body level, leading to an approach known as IM-SRG(2).  This normal-ordered two-body approximation appears to be sufficient in many cases and has yielded excellent results for several nuclei \cite{PhysRevLett.106.222502,PhysRevLett.109.052501,IMSRG}.  The IM-SRG(2) ground state energy is third-order exact, with the most prominent error terms corresponding to fourth order energy diagrams with intermediate triples, and asymmetric intermediate quadruples.  For a wide variety of systems across nuclear physics and quantum chemistry, reincorporation of the triples adds attraction to the system, while that of the asymmetric quadruples adds repulsion.  Because of this cancellation of errors, the IM-SRG(2) tends to track with higher-order methods such as CCSD(T).

Despite the fortuitous result, the cancellation is nonetheless accidental.  A more controlled restoration of the missing error terms can be performed perturbatively.  In Ref.\ \cite{morris2016thesis}, the difference between IM-SRG(2) and perturbative approximations to IM-SRG(3) was investigated in nuclei, the homogeneous electron gas, and several molecules.  In nuclei, differences in binding energies were typically on the order of hundreds of \si{keV}, whereas the binding energies themselves are on the order of \SI{8}{MeV} per nucleon.  This is within the tolerances prescribed by the accuracy of contemporary inter-nucleon interactions.  For electronic systems, the differences were typically less than a few millihartrees.
